MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-21 docs/paper/out/paper.tex
Updated tex/pdf

The MG7 workflow consists of certain steps, each of which perform some
work in parallel, using the cloud infrastructure managed by
\emph{Loquat}. It is important to notice the horizontal scalability of
this approach. Irrespectively of how much data needs to be processed,
MG7 will easily handle it, by splitting data on chunks and performing
the analysis on multiple computation units. The Amazon Elastic Compute
Cloud (EC2) service provides a transparent way of managing computation
infrastructure, called autoscaling groups. The User can set MG7
configuration parameters, adjusting for each task the amount and
hardware characteristics of the EC2 instances they want to occupy for
it. When using Amazon Web Services for parallel computations, it is easy
to scale the computation resources, because the you pay for the time,
not the amount of computation units.

>>>>

The MG7 workflow consists of certain steps, each of which perform some
work in parallel, using the cloud infrastructure managed by
\emph{Loquat}. It is important to notice the horizontal scalability of
this approach. Irrespectively of how much data needs to be processed,
MG7 will easily handle it, by splitting data on chunks and performing
the analysis on multiple computation units. The Amazon Elastic Compute
Cloud (EC2) service provides a transparent way of managing computation
infrastructure, called autoscaling groups. The User can set MG7
configuration parameters, adjusting for each task the amount and
hardware characteristics of the EC2 instances they want to occupy for
it. But it's important to note that as each workflow step is not very
resource demanding, it is not needed to hire EC2 instances with some
advanced hardware, instead an average type will work and you can win
time by simply scaling the number of the hired instances.
